NanoMaLy

### 2015-11-18 paper/pldi16-submission/interactive.tex

\begin{figure*}[t]
\centering
\[
\begin{array}{lcl}
\stepforward{e_i}  &\defeq& {e_{i+1}} \\ \\
\stepbackward{e_i} &\defeq& {e_{i-1}} \\ \\
\jumpforward{e_i} &\defeq& \left\{\begin{array}{ll}
                         e_{i+1}, & \text{if } e_{i+1} = \eapp{v_1}{v_2} \\
                         \jumpforward{e_{i+1}}, & \text{otherwise}
                         \end{array}\right\} \\ \\
\jumpbackward{e_i} &\defeq& \left\{\begin{array}{ll}
                         e_{i-1}, & \text{if } e_{i-1} = \eapp{v_1}{v_2} \\
                         \jumpbackward{e_{i-1}}, & \text{otherwise}
                         \end{array}\right\} \\ \\
\stepinto{e_i} &\defeq& \left\{\begin{array}{ll}
                         e\sub{x}{v_2}, & \text{if } e_i = C[\eapp{v_1}{v_2}] \text{ and } \singlestep{\eapp{v_1}{v_2}}{e\sub{x}{v_2}}
                         \end{array}\right\} \\ \\
\stepover{e_i} &\defeq& \left\{\begin{array}{ll}
                         C[v], & \text{if } e_i = C[\eapp{v_1}{v_2}] \text{ and } \multistep{\eapp{v_1}{v_2}}{v}
                         \end{array}\right\}
\end{array}
\]
\caption{Rules for traversing the reduction graph. \stepintosym and \stepoversym
  require a traversal of the sub-term edges to decompose $e_i$ into the
  target expression \eapp{v_1}{v_2} and the context $C$.
  \ES{need to mention $G$ and $p$ in these rules}
}
\label{fig:traversing-graph}
\end{figure*}

>>>>

\begin{figure*}[t]
\centering
\[
\begin{array}{lcl}
\stepforward{G}{p}{e_i}  &\defeq& \left\{\begin{array}{ll}
    e_j, & \text{where } \singlestep{e_i}{e_j} \in G
                         \end{array}\right\} \\ \\
\stepbackward{G}{p}{e_i}  &\defeq& \left\{\begin{array}{ll}
    e_j, & \text{where } \singlestep{e_j}{e_i} \in G \text{ and } e_j \in p
                         \end{array}\right\} \\ \\
\jumpforward{G}{p}{e_i} &\defeq& \text{let } e_j = \stepforward{G}{p}{e_i} \text{ in }
                         \left\{\begin{array}{ll}
                         e_j, & \text{if } e_j = \eapp{v_1}{v_2} \\
                         \jumpforward{G}{p}{e_{j}}, & \text{otherwise}
                         \end{array}\right\} \\ \\
\jumpbackward{G}{p}{e_i} &\defeq& \text{let } e_j = \stepbackward{G}{p}{e_i} \text{ in }
                         \left\{\begin{array}{ll}
                         e_j, & \text{if } e_j = \eapp{v_1}{v_2} \\
                         \jumpbackward{G}{p}{e_{j}}, & \text{otherwise}
                         \end{array}\right\} \\ \\
\stepinto{G}{p}{e_i} &\defeq& \left\{\begin{array}{ll}
                         e\sub{x}{v_2}, & \text{if } e_i = C[\eapp{v_1}{v_2}] \text{ and } \singlestep{\eapp{v_1}{v_2}}{e\sub{x}{v_2}}
                         \end{array}\right\} \\ \\
\stepover{G}{p}{e_i} &\defeq& \left\{\begin{array}{ll}
                         C[v], & \text{if } e_i = C[\eapp{v_1}{v_2}] \text{ and } \multistep{\eapp{v_1}{v_2}}{v}
                         \end{array}\right\}
\end{array}
\]
\caption{Rules for traversing the reduction graph given a path and
  node. \stepintosym and \stepoversym require a traversal of the
  sub-term edges to decompose $e_i$ into the target expression
  \eapp{v_1}{v_2} and the context $C$.  \ES{these rules are quite ugly and waste space..} }
\label{fig:traversing-graph}
\end{figure*}
